Clustering: A pipeline to analyse time-course gene expression data

### 2019-04-23 scripts/03_clustering.Rmd
Reducing the number of genes for faster clustering

# Whether to filter genes
filter_genes = TRUE
keep_all_significant = FALSE
n_genes_to_keep = 10000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, splines_model,
			colors=as.vector(unlist(ann_colors["Group"])))
```

>>>>

# Whether to filter genes
filter_genes = TRUE
keep_all_significant = FALSE
n_genes_to_keep = 5000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, splines_model,
			colors=as.vector(unlist(ann_colors["Group"])),
			smooth=FALSE)
```
